---
title       : Compare My Car
subtitle    : A Useful Fuel Economy Tool
author      : Emma Shearin
job         : Chief Car Tools Person
framework   : io2012        # {io2012, html5slides, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Applications

What can we do with this tool?

1. Compare old car fuel economies by weight
2. Help consumers decide which car to buy

---  

## Mechanisms

The tool produces a plot based on a customer's entries that compares their current car's weight and fuel economy to the car that they wish to buy, predicting the new car's fuel economy. For example, if the consumer owns a Mazda RX4 and wishes to buy a car weighing 3200 pounds:

```{r, echo= FALSE, results='asis'}
library(datasets)
data(mtcars)
par(pin = c(1.5,1.5), mar = c(8,8,2,2))
# to use data given in example, this code replaces "input$carnum" with q and "input$newcar" with z
q <- 10
z <- 3.2
# generate best fit line and predict the fuel economy of the new car based on input$newcar from ui.R
fit <- lm(mpg ~ wt, mtcars)
pfe <- coef(fit)[1] + (z * coef(fit)[2] )
pwt <- 3.2

# generate comparison line based on consumer's current car
rn <- q
ofe <- mtcars[rn, 1]
owt <- mtcars[rn, 6]

# draw the plot showing the lines at input and predicted values
plot(mtcars$wt, mtcars$mpg, type = "p", main = "Comparison of your selected cars", xlab = "weight (thousands of pounds)", ylab = "fuel economy (mpg)", cex = 5)
abline(fit)
points(y = pfe, x = pwt, col = "blue", pch = 4, cex = 6)
points(y = ofe, x = owt, col = "red", pch = 4, cex = 6)
```

---

## Code

The tool is based on two main functions:

1. Predicting the new fuel economy
2. Plotting data to compare the new data to the old data

The tool uses linear regression to accomplish its prediction and the graphics package in R to plot the data.

---

## Recommendations

This tool works best for people who own one of the 32 car models included in the tool, listed here.
```{r, echo = FALSE}
library(datasets)
data("mtcars")
row.names(mtcars)
```

---
